\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.8in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}  % Remove a numeração das páginas

% Configurações de cores
\definecolor{accent}{RGB}{20,74,128}

% Configuração dos títulos
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]

% Ajuste do espaçamento entre seções
\titlespacing{\section}{0pt}{2.5mm}{2.5mm}
\titlespacing{\subsection}{0pt}{2.5mm}{2.5mm}

% Remover indentação do primeiro parágrafo
\setlength{\parindent}{0pt}

% Hiperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
}

\begin{document}

\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

\begin{center}
    {\Huge \textbf{Roberto Santos Mazutti Kosmel}} \\
    \vspace{1mm}
    {\large Junior Full-Stack Developer \textbar{} React \textbar{} Next.js \textbar{} Node.js (Express) \textbar{} PostgreSQL \textbar{} AWS (EC2, RDS)} \\
    \vspace{1mm}
    São José dos Campos, SP (Remote) \textbar{} \href{mailto:roberto.m.kosmel@gmail.com}{\texttt{roberto.m.kosmel@gmail.com}} \textbar{} +55\,19\,98926-3577 \\
    \href{https://www.linkedin.com/in/robertokosmel/}{\texttt{linkedin.com/in/robertokosmel}} \textbar{} \href{https://github.com/rkosmel}{\texttt{github.com/rkosmel}}
\end{center}

\vspace{2mm}

\section*{Summary}
Junior Full-Stack developer with hands-on experience in production web applications, focused on end-to-end delivery and stability. Work involving React/Next.js, Node.js (Express), and PostgreSQL, with responsibility for deployment and cloud operations (AWS).

\section*{Experience}
\textbf{Software Engineering Intern (Full-Stack)} --- Blue Exams / The Mindville / MBA No Brainer \hfill Apr 2025 — Dec 2025 \\
\begin{itemize}
    \item Built an end-to-end (0->1) subscription-based mock exam web platform, including exam flows (timer, pause/resume, autosave) and analytics.
    \item Created and consumed REST APIs (Next.js endpoints, Stripe, NextAuth, Chatwoot, Node.js backend).
    \item Implemented authentication and subscription billing (NextAuth, Stripe) with PostgreSQL persistence via Prisma.
    \item Supported deployment and production operations on AWS and Linux/Nginx, including troubleshooting and data/asset migration.
\end{itemize}

\section*{Selected Projects}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
    \textbf{Blue Exams --- Mock exam platform} & 2025 \\
\end{tabular*}
\begin{itemize}
    \item End-to-end construction of subscription web platform with exam experience (timer, pause/resume, auto-save) and question review + metrics.
    \item Creation and consumption of REST APIs (Next.js endpoints, Stripe, NextAuth, Chatwoot, Node.js backend).
    \item Authentication/subscription (NextAuth + Stripe), PostgreSQL data (Prisma) and AWS deployment/operations.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
    \textbf{C language compiler} & 2024 \\
\end{tabular*}
\begin{itemize}
    \item Compiler implementation in C (lexical, syntactic and semantic analysis).
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
    \textbf{Electric Ways --- Routes for electric vehicles} & 2024 \\
\end{tabular*}
\begin{itemize}
    \item Route app considering autonomy and charging stops.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
    \textbf{Blue Exams --- Landing page (institutional site)} & 2025 \\
\end{tabular*}
\begin{itemize}
    \item Static site implementation (HTML/CSS/JavaScript) and AWS EC2 + Nginx operation, with TLS/Let's Encrypt.
\end{itemize}

\section*{Education}
\textbf{Federal University of São Paulo (UNIFESP)} --- Computer Engineering (in progress) \hfill 2024 -- Expected Jun 2027 \\
\textbf{Federal University of São Paulo (UNIFESP)} --- Science and Technology (BSc) \hfill 2021 -- 2023

\section*{Skills}
\begin{itemize}
    \item \textbf{Backend}: Node.js, Express, TypeScript/JavaScript, Python, C/C++, REST APIs
    \item \textbf{Frontend}: React, Next.js, TypeScript/JavaScript, HTML5, CSS3, Tailwind CSS
    \item \textbf{Database \& Analysis}: SQL, PostgreSQL, Prisma, JSON, DBeaver, Data Analysis
    \item \textbf{Cloud \& DevOps}: AWS (EC2, RDS, S3 + multiple services), Docker, Nginx, Linux
    \item \textbf{Tools}: Git, Microsoft Office (Advanced), Project Management (Linear, Jira)
    \item \textbf{Automation \& Integrations}: Stripe (payments), Zapier, Twilio, n8n
\end{itemize}

\section*{Languages}
Portuguese (native) \textbar{} English (advanced)

\section*{Extracurricular Activities}
\textbf{University basketball team captain}: leadership, training organization and participation in university tournaments and local competitions.

\end{document}
